The Anatomy of a Temporal Summarization System

### 2015-02-26 experiments.tex
edits; nuggets

Both evaluations make use of the TREC TS data from 2013 and 2014. 
This data includes 25 events and event metadata (e.g., a user
search query for the event, the event type, and event time frame).
Additionally, TREC assessors constructed a set of ground truth facts, or 
nuggets, for each event. The events took place from 20??-20?? and had 
an associated Wikipedia (WP) page. The WP pages were edited and updated 
concurrently with the events, so the diffs between revisions produce a similar
ouput to the ideal update summarization system. Assessors analyzed the diffs
and selected phrases that were important enough to include in an update 
summary.  
For the document stream, we use the news portion of the
 2014 TREC Stream Corpus.
The documents from this corpus come from hourly crawls of the web covering 
 ?, 20?? to ?, 20??. \ckcomment{Need to mention we further filtered the corpus}

>>>>

Both evaluations make use of the TREC TS data from 2013 and 2014. 
This data includes 25 events and event metadata (e.g., a user
search query for the event, the event type, and event timeframe).  All events
occurred during the span of the corpus.

NIST assessors constructed a set of ground truth nuggets for each event. In order
to accomplish this, for each event, assessors were provided with the
revision history of the Wikipedia page associated with the.  For example, 
the revision history for the Wikipedia page for `Hurricane Sandy' will 
contain text additions including those related to individual nuggets.  The assessment
task involves reviewing the Wikipedia revisions in the evaluation timeframe 
and marking the text additions capturing a new, unique nugget.  More detail
on this process can be found in the track description \cite{?}.

For the document stream, we use the news portion of the
 2014 TREC Stream Corpus.
The documents from this corpus come from hourly crawls of the web covering 
 ?, 20?? to ?, 20??. \ckcomment{Need to mention we further filtered the corpus}

### 2015-02-26 introduction.tex
edits; nuggets

In addition to the tight integration between clustering and salience
prediction, our approach also exploits knowledge about the event to determine
salience. Thus, salience does not just represent importance within a set of
documents; it also represents both how typical a sentence is of the  
event
type (i.e., industrial accident, hurricane, riot) and whether it specifies 
information
about this particular event. 
Our feature representation includes a set of language models, one for each
event type, to measure the typicality of the sentence with regard to the 
current event, the distance of mentioned locations from the center of
the event, and the change in word frequencies over the time of the event.
While we ground these features in the domain of disaster, their templates
are generally applicable to many update summarization domains.
% to represent its likelihood of referring to the input disaster. 
%We also utilize the change in word frequencies as we process the stream 
%to measure the changing importance of updates over time.

>>>>

In addition to the tight integration between clustering and salience
prediction, our approach also exploits knowledge about the event to determine
salience. Thus, salience does not just represent importance within a set of
documents; it also represents both how typical a sentence is of the  
event
type (i.e., industrial accident, hurricane, riot) and whether it specifies 
information
about this particular event. 
Our feature representation includes a set of language models, one for each
event type, to measure the typicality of the sentence with regard to the 
current event, the distance of mentioned locations from the center of
the event, and the change in word frequencies over the time of the event.
While we ground these features in the domain of disaster, their templates
are generally applicable to any update summarization task where queries can be classified into types.
% to represent its likelihood of referring to the input disaster. 
%We also utilize the change in word frequencies as we process the stream 
%to measure the changing importance of updates over time.

### 2015-02-26 methods.tex
edits; nuggets

In order to quantify the salience of a sentence with respect to an event,
we assume the event can be represented as a set of atomic facts, or nuggets.
Nuggets are brief and important text snippets that should be conveyed
by an ideal update summary (see Figure~\ref{fig:nuggets} for examples).
\setlength{\fboxsep}{10pt}
\begin{figure}
    \fbox{\parbox{6.9cm}{
        $\cdot$ hurricane force wind warnings are in effect from Rhode Island Sound to Chincoteague Bay\\

@@

Given an update $u$ and a set of nuggets $N$ we define the salience of 
$u$ as,
\[\operatorname{salience}(u) = \operatorname{max}_{n \in N} 
\operatorname{sim}(u, n) \]
where $\operatorname{sim}(\cdot)$ is the semantic similarity \cite{?} (i.e.
the cosine similarity of latent vectors associated with the update and 
nugget text). Since we will not have nuggets for new events, we train
a regression model to predict salience using features derived from 
the updates themselves
and the document stream.

@@

Our system archictecture follows a simple pipeline design where each
stage provides an additional level of processing or filtering of the input
sentences.
At the highest level, we begin with an empty update summary $U$.
At each hour we receive a new batch of sentences $b_t$ from the stream
and perform the following actions:
\begin{enumerate}
    \item predict the salience of sentences in $b_t$ (Section~\ref{sec:salpred}),
  \item select a set of exemplar sentences (by combining clustering with 
      salience predictions) (Section~\ref{sec:exsel}),
  \item add the most novel and salient exemplars to $U$ (Section~\ref{sec:upsel}).
\end{enumerate}

The resultant list of updates $U$ is our summary of the event.
Step 2 uses the affinity propagation algorithm to incorporate the salience
predictions from step 1. For this reason we dub our summarization 
system the \textbf{AP+Salience} model.

@@

After exemplar sentences have been identified, two more filters are applied 
before updating the summary. The exemplars are examined
sequencially in order of highest salience. First, a salience threshold 
is applied, and any exemplars whose salience is less than
$\lambda_{sal}$ are discarded. Second, a similarity threshold 
is applied, where the exemplar is discarded if its
maximum semantic similarity to any previous updates in the summary is
greater than $\lambda_{sim}$. If the exemplar passes these two filters,
it is selected as an update and added to the summary.

>>>>

In order to quantify the salience of a sentence with respect to an event,
we assume the event can be represented as a set of atomic facts, or nuggets.
Nuggets are brief and important text snippets that represent sub-event that should be conveyed
by an ideal update summary (see Figure~\ref{fig:nuggets} for examples).
\setlength{\fboxsep}{10pt}
\begin{figure}
    \fbox{\parbox{6.9cm}{
        $\cdot$ hurricane force wind warnings are in effect from Rhode Island Sound to Chincoteague Bay\\

@@

Given an update $u$ and a set of nuggets $N$ we define the salience of 
$u$ as,
\[\operatorname{salience}(u) = \operatorname{max}_{n \in N} 
\operatorname{sim}(u, n) \]
where $\operatorname{sim}(\cdot)$ is the semantic similarity such as
the cosine similarity of latent vectors associated with the update and 
nugget text \cite{?}. % We train
% a regression model to predict salience using features derived from
% the updates themselves
% and the document stream.

@@

Our system architecture follows a simple pipeline design where each
stage provides an additional level of processing or filtering of the input
sentences.
At the highest level, we begin with an empty update summary $U$.
At each hour we receive a new batch of sentences $b_t$ from the stream
and perform the following actions:
\begin{enumerate}
    \item predict the salience of sentences in $b_t$ (Section~\ref{sec:salpred}),
  \item select a set of exemplar sentences (by combining clustering with 
      salience predictions) (Section~\ref{sec:exsel}),
  \item add the most novel and salient exemplars to $U$ (Section~\ref{sec:upsel}).
\end{enumerate}

The resultant list of updates $U$ is our summary of the event.
Step 2 uses the affinity propagation algorithm to incorporate the salience
predictions from step 1. We refer to this summarization 
system as the \textbf{AP+Salience} model.

@@

After exemplar sentences have been identified, two more filters are applied 
before updating the summary. The exemplars are examined
sequentially in order of highest salience. First, a salience threshold 
is applied, and any exemplars whose salience is less than
$\lambda_{sal}$ are discarded. Second, a similarity threshold 
is applied, where the exemplar is discarded if its
maximum semantic similarity to any previous updates in the summary is
greater than $\lambda_{sim}$. If the exemplar passes these two filters,
it is selected as an update and added to the summary.
